Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-08-08 paper/paper-nature-revised.qmd
final small changes

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as timestamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

@@

Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly. The reason we did not use its `<speech>` child node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days. The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data. For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period of each sitting day in the Chamber where MPs can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

Our approach to parse the `"chamber.xscript"` speeches used in all four scripts meant that all questions without notice content was already parsed in order. For the first two scripts, questions and answers were already separated onto their own rows. For the third and fourth scripts, just as we did with the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers. Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was to extract all question and answer elements from the `"answers.to.questions"` child node.

@@

The next step was to merge Question Time contents with all the debate speech. Our method of parsing meant that everything was already in order, so we did not have to perform any additional merging. For questions in writing, merging this content was also straightforward due to the fact that it is always at the end of Hansard. This means that we could bind question in writing rows to the bottom of the main dataframe. This approach was used for all four scripts.

@@

Once all interjections, comments and continuations were successfully split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists. To do so, we searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus of the user's research does not require stage directions, then this can be removed by filtering observations in `name` equal to "business start", or "stage direction".

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where an MP spoke whose surname was shared by any other past or present MP, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website (https://partyfacts.herokuapp.com). Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/). Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the [Usage Notes](#sec-usage) to follow. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.

>>>>

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions for parsing Federation Chamber proceedings contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as timestamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

@@

Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly. The reason we did not use its `<speech>` child node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days. The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data. For example, the `<talker>` data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period of each sitting day in the Chamber where MPs can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Questions without notice are included directly in the `<chamber.xscript>` child node, with sub-child nodes called `<question>` and `<answer>` to differentiate the two. Questions in writing, however, are embedded in their own child node called `<answers.to.questions>` at the end of the XML file.

Our approach to parse the `<chamber.xscript>` speeches used in all four scripts meant that all questions without notice content was already parsed in order. For the first two scripts, questions and answers were already separated onto their own rows. For the third and fourth scripts, just as we did with the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers. Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was to extract all question and answer elements from the `<answers.to.questions>` child node.

@@

The next step was to merge Question Time contents with all the debate speech. As mentioned, our method of parsing meant that everything was already in order, so we did not have to perform any additional merging for questions without notice content. For questions in writing, merging this content was also straightforward due to the fact that it is always at the end of Hansard. This means that we could bind question in writing rows to the bottom of the main dataframe. This approach was used for all four scripts.

@@

Once all interjections, comments and continuations were split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists. We searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus of the user's research does not require stage directions, then this can be removed by filtering out observations in `name` equal to "business start" or "stage direction".

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (e.g. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where an MP spoke whose surname was shared by any other past or present MP, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining. Example code is provided in the README.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website (https://partyfacts.herokuapp.com). Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/). Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the Usage Notes to follow. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.

### 2023-08-08 paper/paper-nature-revised.tex
final small changes

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{August 3, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, enhanced, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as timestamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

Since the earlier Hansard XMLs do not have a
\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
straightforward way to preserve the ordering of statements and to parse
all speech contents at once was to parse from the
\texttt{\textless{}debate\textgreater{}} element directly. The reason we
did not use its \texttt{\textless{}speech\textgreater{}} child node is
because every speech has a unique structure of node children, and this
makes it difficult to write code for data cleaning which is
generalizable across all speeches and sitting days. The challenge with
parsing through the \texttt{\textless{}debate\textgreater{}} element is
that every piece of data stored in that element is parsed as a single
string, including all \texttt{\textless{}talk.start\textgreater{}} data,
and all nested sub-debate data. For example, the data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{18}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

Our approach to parse the \texttt{"chamber.xscript"} speeches used in
all four scripts meant that all questions without notice content was
already parsed in order. For the first two scripts, questions and
answers were already separated onto their own rows. For the third and
fourth scripts, just as we did with the rest of the speech content, we
used those patterns of data preceding the text to separate questions and
answers. Finally, since questions in writing exist in their own child
node we were able to use the same parsing method for all scripts, which
was to extract all question and answer elements from the
\texttt{"answers.to.questions"} child node.

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts. Despite our
best efforts to capture all stage directions in this list, because it
had to be built manually, users should be aware that it is possible that
some stage directions were not separated onto their own rows in the
process. Further, it is important to note that because they are not
spoken aloud, stage directions do not represent speech components in the
same way that all other components such as interjections and
continuations do. However, they provide valuable information about the
inner-workings and structure of parliamentary events. If the focus of
the user's research does not require stage directions, then this can be
removed by filtering observations in \texttt{name} equal to ``business
start'', or ``stage direction''.

@@

While we did our best to maximize the completeness of the files in our
database as they were processed in the initial four scripts, there were
still a number of rows in which details on the person speaking were
missing, or the name transcribed for that individual was in a short form
(i.e.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
particularly frequent occurrence for sitting days where an MP spoke
whose surname was shared by any other past or present MP, and automated
filling of their details using data from the
\texttt{AustralianPoliticians} package was avoided to prevent any
incorrect detail attribution. In an effort to improve as many of these
as possible, we developed a script which identifies short-form names
belonging to people with common surnames in each CSV, looks for the full
version of that individuals name if available in that same CSV file, and
replaces the short-form name with the full name, and fills the rest of
the MP details in accordingly with data from the
\texttt{AustralianPoliticians} package. This script does the same for
anyone who does have a unique surname but is still missing the full name
form or any gender, unique ID, name ID, party or electorate details.
Each file in our database passed through this script after being
created, to ensure it is as complete as possible.

@@

To enhance the range of research questions which can be explored with
our data, we have created a supplementary file containing debate topics
and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a timestamp. Therefore,
we took the first available page number child-node for each debate or
sub-debate node to be the one we included in our dataset. After
summarizing, these topics can be added to the main text by joining, and
example code is provided in the README.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag those rows where ``The House divided.'' was detected in the body
variable. The \texttt{gender} and \texttt{uniqueID} variables were added
based on the main dataset from the \texttt{AustralianPoliticians}
package, and the \texttt{partyfacts\_id} variable was added using code
and data provided by the Party Facts Project website
(https://partyfacts.herokuapp.com). Note that in accordance with the
code provided on the Party Facts downloads page
(https://partyfacts.herokuapp.com/download/), we used only the core
datasets maintained by the Party Facts project, which are the Manifesto
Project and ParlGov. Details on these datasets can be found on the Party
Facts datasets documentation page
(https://partyfacts.herokuapp.com/documentation/datasets/). Details on
the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
provided in the \protect\hyperlink{sec-usage}{Usage Notes} to follow.
Further, the \texttt{speech\_no} variable allows us to keep track of the
speech number that each statement and interjection belongs to. Having
the speech number variable offers an easy way to group statements by
speech or isolate specific speeches of interest. Lastly, the
\texttt{order} variable was added to maintain the order of proceedings,
after all individual statements were separated onto their own rows.

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{August 8, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, frame hidden, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in
mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions for parsing Federation
Chamber proceedings contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as timestamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

@@

Since the earlier Hansard XMLs do not have a
\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
straightforward way to preserve the ordering of statements and to parse
all speech contents at once was to parse from the
\texttt{\textless{}debate\textgreater{}} element directly. The reason we
did not use its \texttt{\textless{}speech\textgreater{}} child node is
because every speech has a unique structure of node children, and this
makes it difficult to write code for data cleaning which is
generalizable across all speeches and sitting days. The challenge with
parsing through the \texttt{\textless{}debate\textgreater{}} element is
that every piece of data stored in that element is parsed as a single
string, including all \texttt{\textless{}talk.start\textgreater{}} data,
and all nested sub-debate data. For example, the
\texttt{\textless{}talker\textgreater{}} data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{18}. Questions without notice are included directly
in the \texttt{\textless{}chamber.xscript\textgreater{}} child node,
with sub-child nodes called \texttt{\textless{}question\textgreater{}}
and \texttt{\textless{}answer\textgreater{}} to differentiate the two.
Questions in writing, however, are embedded in their own child node
called \texttt{\textless{}answers.to.questions\textgreater{}} at the end
of the XML file.

Our approach to parse the
\texttt{\textless{}chamber.xscript\textgreater{}} speeches used in all
four scripts meant that all questions without notice content was already
parsed in order. For the first two scripts, questions and answers were
already separated onto their own rows. For the third and fourth scripts,
just as we did with the rest of the speech content, we used those
patterns of data preceding the text to separate questions and answers.
Finally, since questions in writing exist in their own child node we
were able to use the same parsing method for all scripts, which was to
extract all question and answer elements from the
\texttt{\textless{}answers.to.questions\textgreater{}} child node.

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts. Despite our
best efforts to capture all stage directions in this list, because it
had to be built manually, users should be aware that it is possible that
some stage directions were not separated onto their own rows in the
process. Further, it is important to note that because they are not
spoken aloud, stage directions do not represent speech components in the
same way that all other components such as interjections and
continuations do. However, they provide valuable information about the
inner-workings and structure of parliamentary events. If the focus of
the user's research does not require stage directions, then this can be
removed by filtering out observations in \texttt{name} equal to
``business start'' or ``stage direction''.

@@

While we did our best to maximize the completeness of the files in our
database as they were processed in the initial four scripts, there were
still a number of rows in which details on the person speaking were
missing, or the name transcribed for that individual was in a short form
(e.g.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
particularly frequent occurrence for sitting days where an MP spoke
whose surname was shared by any other past or present MP, and automated
filling of their details using data from the
\texttt{AustralianPoliticians} package was avoided to prevent any
incorrect detail attribution. In an effort to improve as many of these
as possible, we developed a script which identifies short-form names
belonging to people with common surnames in each CSV, looks for the full
version of that individuals name if available in that same CSV file, and
replaces the short-form name with the full name, and fills the rest of
the MP details in accordingly with data from the
\texttt{AustralianPoliticians} package. This script does the same for
anyone who does have a unique surname but is still missing the full name
form or any gender, unique ID, name ID, party or electorate details.
Each file in our database passed through this script after being
created, to ensure it is as complete as possible.

@@

To enhance the range of research questions which can be explored with
our data, we have created a supplementary file containing debate topics
and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a timestamp. Therefore,
we took the first available page number child-node for each debate or
sub-debate node to be the one we included in our dataset. After
summarizing, these topics can be added to the main text by joining.
Example code is provided in the README.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag those rows where ``The House divided.'' was detected in the body
variable. The \texttt{gender} and \texttt{uniqueID} variables were added
based on the main dataset from the \texttt{AustralianPoliticians}
package, and the \texttt{partyfacts\_id} variable was added using code
and data provided by the Party Facts Project website
(https://partyfacts.herokuapp.com). Note that in accordance with the
code provided on the Party Facts downloads page
(https://partyfacts.herokuapp.com/download/), we used only the core
datasets maintained by the Party Facts project, which are the Manifesto
Project and ParlGov. Details on these datasets can be found on the Party
Facts datasets documentation page
(https://partyfacts.herokuapp.com/documentation/datasets/). Details on
the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
provided in the Usage Notes to follow. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. Lastly, the \texttt{order} variable was added to
maintain the order of proceedings, after all individual statements were
separated onto their own rows.
